Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-12-14 SupportingInformation.Rmd

>>>>

<!--****DAN: Need a 10-panel fig for each one-parameter family showing samples and 
pdfs for 5 values of the parameter. May also need something for the two-parameter
families, but not sure yet how to handle it. After doing the univariate families, then
maybe it is enough to show just the pdf, in which case it can be done in a 
5-by-5 array of panels for the 2-parameter families. That seems like it would work.-->
